The effects of binarity on planet occurrence rates measured by transit surveys

### 2017-12-11 sandbox/derivation.tex
kvetch over normalization. KM's and LB's agree.
Which is nice, because we approached it from two qualitatively different
directions.

In a shell of thickness ${\rm d}r$, there are $n_d(r) 4\pi r^2 {\rm d}r$ 
searchable double star systems.
The number density of searchable double star systems $n_d(r)$ is constant up 
to the maximum searchable distance for singles, $d_0$. At greater distances, 
$n_d(r)$ decreases, because only some binaries have sufficient flux to make 
the SNR cut.
Specifically,
\begin{equation}
n_d(r) = 
\begin{cases}
n_b,	\quad r\leq d_0\\
n_b \int_{q_{\rm min}(r)}^1 {\rm d}q\, f_v(q), \quad d_0 < r < \sqrt{2}d_0 \\
\end{cases}
\end{equation}
where $f_v(q)$ is the mass ratio distribution in a volume-limited sample, 
$q_{\rm min}(r)$ is the minimum mass ratio required to provide sufficient flux 
for searchability.
Assuming $L\propto M^\alpha$,
\begin{equation}
q_{\rm min}(r) =
\left(
    \left( \frac{r}{d_0}\right)^2
    - 1
\right)^{\frac{1}{\alpha}}.
\end{equation}
Using the common parametrization $f_v(q) \sim q^\beta$, and setting $\beta=0$,
\begin{equation}
n_d(r) = 
\begin{cases}
n_b,	\quad r\leq d_0\\
n_b (1-q_{\rm min}(r)), \quad d_0 < r < \sqrt{2}d_0. \\
\end{cases}
\end{equation}
Integrating,
\begin{align}
N_d = \int {\rm d} N_d &= \int n_d(r) 4\pi r^2 {\rm d}r \\
&=
4\pi n_b \left(
    \frac{d_0^3}{3} +
    \left[\frac{r^3}{3}\right]^{\sqrt{2 d_0}}_{d_0}
    -
    \int_{d_0}^{\sqrt{2}d_0} \left(
    \left(\frac{r}{d_0}\right)^2 -1
    \right)^{\frac{1}{\alpha}}
    r^2 \,{\rm d}r
\right) \\
&=
\frac{4 \pi n_b}{3} d_0^3 \left(
2^{3/2} -
3 \int_{1}^{\sqrt{2}} {\rm d}u\, u^2 (u^2 - 1)^{1/\alpha}
\right), \label{eq:dimensionless_integral}
\\
&\equiv
\frac{4 \pi n_b}{3} d_0^3 \left(
2^{3/2} - 3 I
\right),
\end{align}
where the penultimate line substituted $u=r/d_0$.
For the common case $\alpha=3.5$, the dimensionless integral $I$ evaluates to 
$\approx 0.484174$.

@@

@@

%TODO: PROCEED FROM HERE

@@

Since we assume $\ps\a=\ps_1$,
\begin{equation}
	\mathcal{N}_{\rm s}^1(r_a, M_a; r, M) \propto \delta(M_a-M).
\end{equation}
In this case, $\mathcal{N}_{\rm s}^1$ is non-zero only at 
$r_a=R_a\sqrt{\delta_{\rm obs}}$, 
and the observed depth is
\begin{equation}
	\delta_{\rm obs}
	= \left[{r\over R(M_a)}\right]^2\times {L(M_a) \over L_{\rm sys}(M_a, q)}.
   \label{eq:delta_obs_primaries} 
\end{equation}
The normalization of $\mathcal{N}_{\rm s}^1$ is given by the number of 
binaries that are searchable for a signal $\delta_{\rm obs}$:
\begin{equation}
	N_{\rm s}^0(\delta_{\rm obs}, 
	L(M_a))\cdot\mu(\mathrm{BF},M_a).
\end{equation}
Thus, the number of primaries with apparent parameters $(r_a,M_a)$ given the 
true parameters $(r,M)$ is
\begin{equation}
	\mathcal{N}_{\rm s}^1(r_a, M_a; r, M)
	=\int \mathrm{d}q\,f(q)\mathcal{N}_{{\rm s}, q}^1(r_a, M_a; r, M; q),
    \label{eq:fancyN_s_1}
\end{equation}
where $f(q)$ is the binary mass ratio distribution in the SNR-limited sample 
and
\begin{align}
	\notag
	\mathcal{N}_{{\rm s}, q}^1(r_a, M_a; r, M; q)
	&=N_{\rm s}^0(\delta_{\rm obs}, L(M_a))\cdot\mu(\mathrm{BF},M_a)\\
	&\times\delta \left(r_a-r\sqrt{{L(M_a) \over L_{\rm sys}(M_a, 
	q)}}\right)\delta(M_a-M).
\label{eq:N_s_1}
\end{align}
Note that while the observed depth is a function of the true parameters 
(Eq.~\ref{eq:delta_obs_primaries}), since we are counting 
detected planets of a given {\it apparent} size, we will not need to worry 
about this dependence.
As discussed in the main text, in Eq.~\ref{eq:fancyN_s_1} we will have $f(q) 
\sim q^\beta (1+q^\alpha)^{3/2}$.

@@

In this case, $M=qM_1=qM_a$, so
\begin{equation}
	\mathcal{N}_{\rm s}^2(r_a, M_a; r, M)
	\propto \delta\left(M_a-{M\over q}\right).
    \label{eq:fancyN_s_2_prop}
\end{equation}
Again $\mathcal{N}_{\rm s}^2$ is non-zero only at $r_a=R_a\sqrt{\delta_{\rm 
obs}}$, but this 
time
\begin{equation}
	\delta_{\rm obs} = \left[{r\over R(qM_a)}\right]^2 \times {L(qM_a) 
	\over L_{\rm sys}(M_a, q)}.
\end{equation}
The normalization remains the same as the previous case (we are counting the 
searchable stars at a given observed depth $\delta_{\rm obs}$, total 
luminosity of the binary is the same).
Thus,
\begin{equation}
	\mathcal{N}_{\rm s}^2(r_a, M_a; r, M)
	=\int \mathrm{d}q\,f(q)\mathcal{N}_{{\rm s}, q}^2(r_a, M_a; r, M; q),
\end{equation}
where
\begin{align}
	\notag
	\mathcal{N}_{\rm s}^2(r_a, M_a; r, M; q)
	%&=N_{\rm s}(\delta_{\rm obs}, L(M_a)) \left[L_{\rm sys}(M_a, q) \over 
	%L(M_a) 
	%\right]^{3/2}\\
	&=N_{\rm s}^0(\delta_{\rm obs}, L(M_a))\cdot\mu(\mathrm{BF},M_a)\\
	&\times \delta \left(r_a-r\sqrt{ \left[{R(M_a)\over R(qM_a)}\right]^2 
	{L(qM_a) 
	\over L_{\rm sys}(M_a, q)} }\right)\delta\left(M_a-{M\over q}\right).
\end{align}

@@

@@

\begin{align}
	N_{\rm det}^1(r\a, M\a)
	&=\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_{\rm s}^1(r\a, M\a; r, M)
	\cdot\Gamma^1(r, M) \cdot p_{\rm tra}(M)\\
	&=\int \mathrm{d}q\,f(q)\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_{{\rm s}, 
	q}^1(r\a, M\a; r, M; q)\cdot\Gamma^1(r, M) \cdot p_{\rm tra}(M)\\
	&=N\s^0(\delta_{\rm obs}, L(M\a))\cdot p_{\rm tra}(M\a) \cdot
	\mu(\mathrm{BF}, M\a) \int {\mathrm{d}q \over 
	\mathcal{A}}\,f(q)\,\Gamma^1(r_a/\mathcal{A}, M\a),
	%\left[L_{\rm sys}(M_a, q) \over L(M_a) \right]^{3/2},
\end{align}
where
\begin{equation}
	\mathcal{A}(q, M\a)=\sqrt{L(M\a) \over L_{\rm sys}(M\a, q)}.
\end{equation}

Finally,
\begin{align}
	N_{\rm det}^2(r\a, M\a)
	&=\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_{\rm s}^2(r\a, M\a; r, M)
	\cdot\Gamma^2(r, M) \cdot p_{\rm tra}(M)
    \\
	&=\int \mathrm{d}q\,f(q)\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_{{\rm s}, 
	q}^2(r\a, M\a; r, M; q)\cdot\Gamma^2(r, M) \cdot p_{\rm tra}(M)
    \\
    &= N\s^0(\delta_{\rm obs},L(M\a)) \mu({\rm BF},M\a)
    \int {\rm d}r{\rm d}q\, q f(q) \delta(r_a - r\mathcal{B}) 
    \Gamma^2(r,qM\a) 
    p_{\rm tra}(qM\a) \\
	&=%N_{\rm s}(\delta_{\rm obs}, L(M_a)
	N\s^0(\delta_{\rm obs}, L(M\a))\cdot\mu(\mathrm{BF}, M\a)
	\int {q \mathrm{d}q \over \mathcal{B}}\,f(q)\,\Gamma^2(r_a/\mathcal{B}, 
	qM\a)\,p_{\rm 
	tra}(qM\a),
	%\left[L_{\rm sys}(M_a, q) \over L(M_a) \right]^{3/2},
\end{align}
where
\begin{equation}
	\mathcal{B}(q, M\a)={R(M\a)\over R(qM\a)}\sqrt{{L(qM\a) \over L_{\rm 
	sys}(M\a, q)} }.
\end{equation}

@@

Note again that the denominators of $\Gamma\a$ are the same for singles, 
primaries, and secondaries: $N_{\rm s,a}(\delta_{\rm obs}, M\a)$ and $p_{\rm 
tra}(M\a)$. This is because we are calculating the occurrence at the same 
apparent planet/star properties, and the observer can never distinguish 
binaries from singles (and adopt the primary properties for binaries).
Using the results above, the apparent rate density,
\begin{align}
\Gamma\a(r\a,M\a) &= 
    \frac{1}{N_{\rm s,a}(r\a,M\a) p_{\rm tra}(r\a,M\a)} \times
    \sum_i N_{\rm det}^i (r\a,M\a),
\end{align}
evaluates to
\begin{align}
\notag
\Gamma\a(r\a,M\a) &= {1\over 1+\mu(\mathrm{BF}, M\a)}\times
   \left\{ \Gamma^0(r\a, M\a)+ 
\mu(\mathrm{BF}, M\a)
\left[ \int {\mathrm{d}q \over \mathcal{A}}\,f(q)\,\Gamma^1\left({r\a\over 
    \mathcal{A}}, 
M\a\right)\,
\right.   
   \right. \\
& \quad\quad\quad\quad\quad \left.\left.
+\int {q \mathrm{d}q \over \mathcal{B}}\,f(q)\,\Gamma^2\left({r\a\over 
\mathcal{B}}, 
qM\a\right)\,
{R(qM\a) \over R(M\a)}
q^{-1/3} \right]	\right\}.  
\end{align}

>>>>

In a shell of thickness ${\rm d}r$, there are $n_d(r) 4\pi r^2 {\rm d}r$ 
searchable double star systems.
The number density of searchable double star systems $n_d(r)$ is constant up 
to the maximum searchable distance for singles, $d_0$. At greater distances, 
$n_d(r)$ decreases, because only some binaries have sufficient flux to make 
the SNR cut.
Specifically,
\begin{equation}
n_d(r) = 
\begin{cases}
n_b,	\quad r\leq d_0\\
n_b \int_{q_{\rm min}(r)}^1 {\rm d}q\, f_{\rm vl}(q), \quad d_0 < r < 
\sqrt{2}d_0 \\
\end{cases}
\end{equation}
where $f_{\rm vl}(q)$ is the mass ratio distribution in a volume-limited 
sample, $q_{\rm min}(r)$ is the minimum mass ratio required to provide 
sufficient flux for searchability.
Assuming $L\propto M^\alpha$,
\begin{equation}
q_{\rm min}(r) =
\left(
    \left( \frac{r}{d_0}\right)^2
    - 1
\right)^{\frac{1}{\alpha}}.
\end{equation}
Using the common parametrization $f_v(q) \sim q^\beta$, and setting $\beta=0$,
\begin{equation}
n_d(r) = 
\begin{cases}
n_b,	\quad r\leq d_0\\
n_b (1-q_{\rm min}(r)), \quad d_0 < r < \sqrt{2}d_0. \\
\end{cases}
\end{equation}
Integrating,
\begin{align}
N_d = \int {\rm d} N_d &= \int n_d(r) 4\pi r^2 {\rm d}r \\
&=
4\pi n_b \left(
    \frac{d_0^3}{3} +
    \left[\frac{r^3}{3}\right]^{\sqrt{2 d_0}}_{d_0}
    -
    \int_{d_0}^{\sqrt{2}d_0} \left(
    \left(\frac{r}{d_0}\right)^2 -1
    \right)^{\frac{1}{\alpha}}
    r^2 \,{\rm d}r
\right) \\
&=
\frac{4 \pi n_b}{3} d_0^3 \left(
2^{3/2} -
3 \int_{1}^{\sqrt{2}} {\rm d}u\, u^2 (u^2 - 1)^{1/\alpha}
\right), \label{eq:dimensionless_integral}
\\
&\equiv
\frac{4 \pi n_b}{3} d_0^3 \left(
2^{3/2} - 3 I
\right),
\end{align}
where the penultimate line substituted $u=r/d_0$.
For the common case $\alpha=3.5$, the dimensionless integral $I$ evaluates to 
$\approx 0.484174$.

@@

\subsubsection{Alternative Derivation of $\mu$}

For a given set of $(\delta_{\rm obs}, M\a)$  and $q$, the searchable distance for binaries is larger than singles by $\sqrt{1+L(qM\a)/L(M\a)}$. Thus,
\begin{equation}
	{N_d \over N_s^0}=\int_0^1 {n_b\over n_s}\left[1+{L(qM\a) \over L(M\a)}\right]^{3/2} f(q)\mathrm{d}q
	=\int_0^1 \frac{{\rm BF}}{1 - {\rm BF}}\left[1+{L(qM\a) \over L(M\a)}\right]^{3/2} f(q)\mathrm{d}q.
\end{equation}
If $\mathrm{BF}$ is independent of $q$, $L\sim M^\alpha$, and $f(q)\sim q^\beta$:
\begin{equation}
	{N_d \over N_s^0}
	=\frac{{\rm BF}}{1 - {\rm BF}}\cdot {1\over{1+\beta}}\int_0^1 \left(1+q^\alpha\right)^{3/2} q^\beta\mathrm{d}q,
\end{equation}
which may be written in a closed form using the hypergeometric function. 
Integrating by parts and using $u\equiv(1+q^\alpha)^{1/2}$, this reduces to
\begin{align}
	{N_d \over N_s^0}
	\notag
	&=\frac{{\rm BF}}{1 - {\rm BF}} \left(1\over{1+\beta}\right)^2
	\left\{
	\left[q^{\beta+1}\left(1+q^\alpha\right)^{3/2}\right]_0^1-{3\over2}\alpha \int_0^1 q^{\alpha+\beta}\left(1+q^\alpha\right)^{1/2} \mathrm{d}q \right\},\\
	&=\frac{{\rm BF}}{1 - {\rm BF}} \left(1\over{1+\beta}\right)^2
	\left[ 2^{3/2} - 3 \int_1^{\sqrt{2}} u^2(u^2-1)^{{1+\beta}\over\alpha}\mathrm{d}u \right].
\end{align}
For $\beta=0$, the last line is equivalent to Eq.(14).

@@

@@

The number of primaries with apparent parameters $(r_a,M_a)$ given the 
true parameters $(r,M)$ is
\begin{equation}
	\mathcal{N}_{\rm s}^1(r_a, M_a; r, M)
	=\int \mathrm{d}q\,f(q)\mathcal{N}_{{\rm s}, q}^1(r_a, M_a, q; r, M),
    \label{eq:fancyN_s_1}
\end{equation}
where $f(q)$ is the binary mass ratio distribution.

Since we assume $\ps\a=\ps_1$,
\begin{equation}
	\mathcal{N}_{{\rm s},q}^1(r_a, M_a, q; r, M) \propto \delta(M_a-M).
\end{equation}
In this case, $\mathcal{N}_{{\rm s},q}^1$ is non-zero only at 
$r_a=R_a\sqrt{\delta_{\rm obs}}$, 
and the observed depth is
\begin{equation}
	\delta_{\rm obs}
	= \left[{r\over R(M_a)}\right]^2\times {L(M_a) \over L_{\rm sys}(M_a, q)}
	\equiv \left[{r\over R(M_a)}\right]^2\times \mathcal{A}(q,M\a)^2
   \label{eq:delta_obs_primaries} 
\end{equation}
The normalization of $\mathcal{N}_{{\rm s},q}^1$ is given by the number of 
binaries that are searchable for a signal $\delta_{\rm obs}$ and have the mass ratio $q$ (cf. 1.3.2):
\begin{equation}
	N_{\rm s}^0(\delta_{\rm obs}, 
	L(M_a))\cdot
	{n_b\over n_s}\left[L_{\rm sys}(M_a, q) \over L(M\a)\right]^{3/2}
	=N_{\rm s}^0(\delta_{\rm obs}, L(M_a))
	\cdot \frac{{\rm BF}}{1 - {\rm BF}} \cdot {1 \over \mathcal{A}(q,M\a)^3}.
    \label{eq:primary_normalization}
\end{equation}

Thus,
\begin{align}
	\notag
	\mathcal{N}_{{\rm s}, q}^1(r_a, M_a, q; r, M)
	&=N_{\rm s}^0(\delta_{\rm obs}, L(M_a))
	\cdot \frac{{\rm BF}}{1 - {\rm BF}} \cdot {1 \over \mathcal{A}(q,M\a)^3}\\
	&\times\delta \left[r_a-r\mathcal{A}(q,M\a)\right]\delta(M_a-M).
	%&=N_{\rm s}^0(\delta_{\rm obs}, L(M_a))\cdot\mu(\mathrm{BF},M_a)\\
	%&\times\delta \left(r_a-r\sqrt{{L(M_a) \over L_{\rm sys}(M_a, q)}}\right)\delta(M_a-M).
\label{eq:N_s_1}
\end{align}
Note that while the observed depth is a function of the true parameters 
(Eq.~\ref{eq:delta_obs_primaries}), since we are counting 
detected planets of a given {\it apparent} size, we will not need to worry 
about this dependence.
In Eq.~\ref{eq:fancyN_s_1}, we will have $f(q) \sim q^\beta $, the 
volume-limited mass ratio distribution (Eq.~\ref{eq:primary_normalization} 
accounts for the Malmquist bias).

@@

In this case, $M=qM_1=qM_a$, so
\begin{equation}
	\mathcal{N}_{{\rm s},q}^2(r_a, M_a, q; r, M)
	\propto \delta\left(M_a-{M\over q}\right).
    \label{eq:fancyN_s_2_prop}
\end{equation}
Again $\mathcal{N}_{\rm s}^2$ is non-zero only at $r_a=R_a\sqrt{\delta_{\rm 
obs}}$, but this 
time
\begin{equation}
	\delta_{\rm obs} = \left[{r\over R(qM_a)}\right]^2 \times {L(qM_a) 
	\over L_{\rm sys}(M_a, q)}.
\end{equation}
The normalization remains the same as the previous case (we are counting the 
searchable stars at a given observed depth $\delta_{\rm obs}$, total 
luminosity of the binary is the same).
Thus,
\begin{equation}
	\mathcal{N}_{\rm s}^2(r_a, M_a; r, M)
	=\int \mathrm{d}q\,f(q)\mathcal{N}_{{\rm s}, q}^2(r_a, M_a, q; r, M),
\end{equation}
where
\begin{align}
	\notag
	\mathcal{N}_{\rm s}^2(r_a, M_a; r, M; q)
	%&=N_{\rm s}^0(\delta_{\rm obs}, L(M_a))\cdot\mu(\mathrm{BF},M_a)\\
	&=N_{\rm s}^0(\delta_{\rm obs}, L(M_a)) \cdot \frac{{\rm BF}}{1 - {\rm BF}} \cdot {1 \over \mathcal{A}(q,M\a)^3}\\
	&\times \delta \left(r_a-r\sqrt{ \left[{R(M_a)\over R(qM_a)}\right]^2 
	{L(qM_a) 
	\over L_{\rm sys}(M_a, q)} }\right)\delta\left(M_a-{M\over q}\right).
\label{eq:mathcal_N_s_2}
\end{align}

@@

One might also worry because in Eq.~\ref{eq:mathcal_N_s_2}, it is hard to see 
any explicit indication that secondaries are harder to search for planets of a 
given true size than primaries (or singles).
This piece of intuition is accounted in the delta functions.
If one were to instead go through the exercise of saying ``how many searchable 
secondaries are there in terms of the {\it true} parameters?'' you would get 
exactly the same answer\footnote{LB did this, in his handwritten notes
\texttt{2017/12/09.0-2017/12/11/.0}}.

@@

\begin{align}
	N_{\rm det}^1(r\a, M\a)
	&=\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_{\rm s}^1(r\a, M\a; r, M)
	\cdot\Gamma^1(r, M) \cdot p_{\rm tra}(M)\\
	&=\int \mathrm{d}q\,f(q)\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_{{\rm s}, 
	q}^1(r\a, M\a, q; r, M)\cdot\Gamma^1(r, M) \cdot p_{\rm tra}(M)\\
	&=N\s^0(\delta_{\rm obs}, L(M\a))\cdot p_{\rm tra}(M\a) \cdot
	{\mathrm{BF}\over{1-\mathrm{BF}}} \int {\mathrm{d}q \over 
	\mathcal{A}^4}\,f(q)\,\Gamma^1\left({r_a\over\mathcal{A}}, M\a\right),
\end{align}
where
\begin{equation}
	\mathcal{A}(q, M\a)=\sqrt{L(M\a) \over L_{\rm sys}(M\a, q)}.
\end{equation}

Finally,
\begin{align}
	N_{\rm det}^2(r\a, M\a)
	&=\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_{\rm s}^2(r\a, M\a; r, M)
	\cdot\Gamma^2(r, M) \cdot p_{\rm tra}(M)\\
	&=\int \mathrm{d}q\,f(q)\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_{{\rm s}, 
	q}^2(r\a, M\a, q; r, M)\cdot\Gamma^2(r, M) \cdot p_{\rm tra}(M)\\
    &= N\s^0(\delta_{\rm obs},L(M\a)) \cdot \frac{{\rm BF}}{1 - {\rm BF}}
    \int {{\rm d}r{\rm d}q\over \mathcal{A}^3}\, q f(q) \delta(r_a - r\mathcal{B}) 
    \Gamma^2(r,qM\a) 
    p_{\rm tra}(qM\a) \\
	&=%N_{\rm s}(\delta_{\rm obs}, L(M_a)
	N\s^0(\delta_{\rm obs}, L(M\a))\cdot \frac{{\rm BF}}{1 - {\rm BF}}
	\int {q \mathrm{d}q \over {\mathcal{A}^3\mathcal{B}}}\,f(q)\,\Gamma^2(r_a/\mathcal{B}, 
	qM\a)\,p_{\rm 
	tra}(qM\a),
	%\left[L_{\rm sys}(M_a, q) \over L(M_a) \right]^{3/2},
\end{align}
where
\begin{equation}
	\mathcal{B}(q, M\a)={R(M\a)\over R(qM\a)}\sqrt{{L(qM\a) \over L_{\rm 
	sys}(M\a, q)} }.
\end{equation}

@@

Note again that the denominators of $\Gamma\a$ are the same for singles, 
primaries, and secondaries: $N_{\rm s,a}(\delta_{\rm obs}, M\a)$ and $p_{\rm 
tra}(M\a)$. This is because we are calculating the occurrence at the same 
apparent planet/star properties, and the observer can never distinguish 
binaries from singles (and adopt the primary properties for binaries).
Using the results above, the apparent rate density,
\begin{align}
\Gamma\a(r\a,M\a) &= 
    \frac{1}{N_{\rm s,a}(r\a,M\a) p_{\rm tra}(r\a,M\a)} \times
    \sum_i N_{\rm det}^i (r\a,M\a),
\end{align}
evaluates to
\begin{align}
\notag
\Gamma\a(r\a,M\a) &= {1\over 1+\mu(\mathrm{BF}, M\a)}\times
   \left\{ \Gamma^0(r\a, M\a)+ 
\frac{{\rm BF}}{1 - {\rm BF}}
\left[ \int {\mathrm{d}q \over \mathcal{A}^4}\,f(q)\,\Gamma^1\left({r\a\over 
    \mathcal{A}}, 
M\a\right)\,
\right.   
   \right. \\
& \quad\quad\quad\quad\quad \left.\left.
+\int {q \mathrm{d}q \over {\mathcal{A}^3\mathcal{B}}}\,f(q)\,\Gamma^2\left({r\a\over 
\mathcal{B}}, 
qM\a\right)\,
{R(qM\a) \over R(M\a)}
q^{-1/3} \right]	\right\}.  
\end{align}

\edit1{MODIFIED UP TO THIS POINT}

\edit2{TODO: follow the above analytics to below limiting cases}
